### 2021-12-15 documentos/pce.tex
dandole

As mentioned above, \pce{} maps nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\label{eq:definition:Pauli}
\end{equation}
Similar to the qubit case, not every operation with this form is a \cptp{} map. For the operation to be trace preserving, it is easy to prove that $\tau_{\vec 0}=1$. In the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper.

A Pauli component erasing (PCE) operation is a Pauli diagonal operation
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
 determine which $\taus$ lead to a valid quantum map.

@@

A graphical representation for PCE maps may be introduced, being the
two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
\eref{eq:N_qubits_rho}. For a given PCE, we shall fill 
the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
for two qubits, we exemplify them in \fref{fig:two:qubit:examples}.

\cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
frases de la importancia de esta familia.} \ddnote{hecho}.
% Notice
% than in both cases we drop the label $\alpha$ for simplicity, as it will 
% remain unchanged throughout this text \janote{No entiendo qué estás diciendo
% aquí}.

>>>>

As mentioned above, \pce{} maps nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1,
\label{eq:definition:Pauli}
\end{equation}
with $\tau_{\vec k}$ either $1$ or $0$.
Similar to the qubit case, not every operation with this form is a \cptp{} map. For the operation to be trace preserving, it is easy to prove that $\tau_{\vec 0}=1$. On the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper. Moreover, these operations are by definition diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$ basis.

It is worth noticing that the set of \pce{} maps overlaps with the set of ``Pauli diagonal channels constant on axes'' defined in Ref.~\cite{nathanson2007pauli}, consisting of convex combinations of \textit{quantum-classical} channels. In particular, it can be shown that quantum-classical channels defined with the eigenbasis of some set of $2^N-1$ commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $ 2^N $ components equal to $1$s in its diagonal.

\cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
frases de la importancia de esta familia.} \ddnote{hecho, pero de pronto quedo espeso. Me estan gustando las cosas que he estado encontrando, voy a investigar en esa direccion por mi cuenta, si sale algo interesante, los invito, como no}

@@

For the two qubits case, the operations illustrated in~\eref{eq:definition:Pauli} can be pictured using $4\times 4$ tables, showing the positions of the $0$s and $1$s of the diagonal using the Pauli string basis, see~\fref{fig:two:qubit:examples}. This way of representing \pce{} maps turned out to be very useful for their analysis throughout this work.

% Notice
% than in both cases we drop the label $\alpha$ for simplicity, as it will 
% remain unchanged throughout this text \janote{No entiendo qué estás diciendo
% aquí}.
